---
title: "Scenario 2: CKMR simulation results: 100% biennial female breeders + 5% non-conformists"
output: 
  html_document:
    df_print: tibble
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
#devtools::install_github("pconn/HierarchicalGOF/HierarchicalGOF")
#install.packages("ggmcmc")
```

```{r read-in-files, include=FALSE}
library(tidyverse)
library(ggpubr)
library(RColorBrewer)
library(coda)
library(runjags)
library(ggmcmc)
library(viridis)

rm(list=ls())
today <- format(Sys.Date(), "%d%b%Y")
purpose.combo <- "Determine_optimal_sampling_scheme_and_performance_w_psi_and_surv" #What am I comparing right now? This will be used to name output files


#----------------Read in files ------------------------------
#------------- MCMC parameters ----------------#
ni <- 40000 # number of post-burn-in samples per chain
nb <- 50000 # number of burn-in samples
nt <- 20     # thinning rate
nc <- 2      # number of chains
MCMC.settings <- paste0("thin", nt, "_draw", ni, "_burn", nb)

#Initialize values
purpose1.lab = purpose2.lab = purpose3.lab = purpose4.lab <- NULL

#------------- Simulation parameters and labels  ----------------#
date.of.simulation1 <- "09May2022"
purpose1 <- "HS.only_target.YOY_SimPsi1_0.5NonConform_uninf.priors"
purpose1.lab <- "Targeted sampling - uninformative priors on survival and psi"
model.type1 <- "HS.only"

date.of.simulation2 <- "09May2022"
purpose2 <- "HS.only_target.YOY_SimPsi1_0.05NonConform_informative.priors"
purpose2.lab <- "Targeted sampling - informed prior on survival; psi fixed"
model.type2 <- "HS.only"

date.of.simulation3 <- "09May2022"
purpose3 <- "HS.only_sample.all.ages_SimPsi1_0.05NonConform_uninf.priors"
purpose3.lab <- "All ages sampled - uninformative priors on survival and psi"
model.type3 <- "HS.only"

date.of.simulation4 <- "09May2022"
purpose4 <- "HS.only_sample.all.ages_SimPsi1_0.05NonConform_informative.priors"
purpose4.lab <- "All ages sampled - informed prior on survival; psi fixed"
model.type4 <- "HS.only"

seeds <- "Seeds2022.04.15"
sim.samples.1 <- "0.5prop.sampled" #Label on file output
samples1.lab <- "0.5 percent sampled" #Label for dataframe and figures
sim.samples.2 <- "1prop.sampled" #Label on file output
samples2.lab <- "1 percent sampled" #Label for dataframe and figures
sim.samples.3 <- "1.5prop.sampled"  #Label on file output
samples3.lab <- "1.5 percent sampled" #Label for dataframe and figures
sim.samples.4 <- "2prop.sampled" #Label on file output
samples4.lab <- "2 percent sampled" #Label for dataframe and figures
sim.samples.all <- c(0.5, 1, 1.5, 2) #This is the number of samples when sampling specific proportions of the juvenile population for the HS only model. Current as of 05/03/2022

sim.samples.labs.all <- c(samples1.lab, samples2.lab, samples3.lab, samples4.lab)

MCMC_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.construction/Model.output/"
results_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.construction/Model.results/"
results_plots_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.construction/Model.results/figures/"
results_prefix <- "CKMR_results"
MCMC_prefix <- "CKMR_modelout"
parents_prefix <- "parents_breakdown/CKMR_parents.breakdown"
sample.prefix <- "sample_info/CKMR_sample.info"
survival.prefix <- "survival/CKMR_survival"
pop.size.prefix <- "pop_size/CKMR_pop.size"
mom.comps.prefix <- "comparisons/mom.comps"
dad.comps.prefix <- "comparisons/dad.comps"


#Set results to NULL and the script will run regardless of how many actual results are being compared
results.1 = results.2 = results.3 = results.4 <- NULL

results.1 <- read_csv(paste0(results_location, results_prefix, "_", date.of.simulation1, "_", seeds, "_", purpose1, ".csv")) %>% 
  mutate(model_type = model.type1, 
         purpose.lab = purpose1.lab) %>% 
  mutate(total_samples = total_juvenile_samples + total_adult_samples)

results.2 <- read_csv(paste0(results_location, results_prefix, "_", date.of.simulation2, "_", seeds, "_", purpose2, ".csv")) %>% 
  mutate(model_type = model.type2,
         purpose.lab = purpose2.lab) %>% 
    mutate(total_samples = total_juvenile_samples + total_adult_samples)


results.3 <- read_csv(paste0(results_location, results_prefix, "_", date.of.simulation3, "_", seeds, "_", purpose3, ".csv")) %>% 
  mutate(model_type = model.type3,
         purpose.lab = purpose3.lab) %>% 
      mutate(total_samples = total_juvenile_samples + total_adult_samples)

results.4 <- read_csv(paste0(results_location, results_prefix, "_", date.of.simulation4, "_", seeds, "_", purpose4, ".csv")) %>% 
    mutate(model_type = model.type4,
           purpose.lab = purpose4.lab) %>% 
      mutate(total_samples = total_juvenile_samples + total_adult_samples)
```

```{r Quick-analysis-of-results, echo = FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
####------------------------------- Quick analysis of results -----------------------------------####

results.all <- results.1 %>% 
  bind_rows(results.2, results.3, results.4) %>% 
  #mutate(total_samples = total_juvenile_samples + total_adult_samples) %>% 
  #mutate(relative_bias = round(((Q50 - truth)/truth)*100,1)) %>%
  #mutate(in_interval = ifelse(HPD2.5 < truth & truth < HPD97.5, "Y", "N")) %>% 
  mutate(cv = (sd/mean)*100) %>% 
  mutate(samples.lab = paste0(prop_sampled_juvs, " percent sampled")) %>% 
  separate(col = purpose.lab, into = "sampling.scheme", sep = " -", remove = FALSE)

results.all$samples.lab <- factor(results.all$samples.lab, levels = c(samples1.lab, samples2.lab, samples3.lab, samples4.lab))

results.all$purpose.lab <- factor(results.all$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))

#Specify parameters
#jags_params <- c("Nfa", "Nfb", "Nm", "surv", "lam", "psi", "pb") #if estimating all parameters with the HS|PO model
jags_params <- c("Nfb", "psi", "Nm", "surv", "lam") #If estimating all parameters with the HS only model

#Save instances that failed to converge so they can be removed later from the HPDI dataframes
no.convergence <- results.all %>% dplyr::filter(Rhat > 1.01) %>% 
  mutate(purp = ifelse(purpose.lab == purpose1.lab, 1,
                       ifelse(purpose.lab == purpose2.lab, 2,
                              ifelse(purpose.lab == purpose3.lab, 3, 4)))) %>% 
  mutate(samps = ifelse(total_samples == sim.samples.all[1], 1,
                        ifelse(total_samples == sim.samples.all[2], 2,
                               ifelse(total_samples == sim.samples.all[3], 3, 4)))) %>% 
  distinct(purpose.lab, purp, total_samples, iteration, samps)

#Print the number of instances that failed to converge
cat(paste0("Of the ", nrow(results.all), " parameter estimates from these simulations, ", nrow(no.convergence), " instances failed to converge at Rhat > 1.01"))

#Remove instances that failed to converge
results.all <- results.all %>% dplyr::filter(Rhat < 1.01)

#Any other metrics to show here?
```

```{r Calcualte HPDI intervals, echo=FALSE}
#Read in previously saved file
HPD.1.summary_all <- read_csv(file = paste0(results_location, "HPD.summaries/HPD.summary_", date.of.simulation1, "_", purpose1, ".csv"))

HPD.1.summary.tidy <- HPD.1.summary_all %>% 
  pivot_longer(
    cols = starts_with("percent"),
    names_to = "proportion_sampled",
    names_prefix = "percent_in_interval.",
    values_to = "percent_in_interval"
    ) %>% 
  mutate(model_type = model.type1,
         purpose.lab = purpose1.lab)

#---------------------------Purpose 2 --------------------------------#    
#Read in previously saved file
HPD.2.summary_all <- read_csv(file = paste0(results_location, "HPD.summaries/HPD.summary_", date.of.simulation2, "_", purpose2, ".csv"))

HPD.2.summary.tidy <- HPD.2.summary_all %>% 
  pivot_longer(
    cols = starts_with("percent"),
    names_to = "proportion_sampled",
    names_prefix = "percent_in_interval.",
    values_to = "percent_in_interval"
  ) %>% 
  mutate(model_type = model.type2,
                  purpose.lab = purpose2.lab)

#---------------------------Purpose 3 --------------------------------#    

#Read in previously saved file
HPD.3.summary_all <- read_csv(file = paste0(results_location, "HPD.summaries/HPD.summary_", date.of.simulation3, "_", purpose3, ".csv"))

HPD.3.summary.tidy <- HPD.3.summary_all %>% 
  pivot_longer(
    cols = starts_with("percent"),
    names_to = "proportion_sampled",
    names_prefix = "percent_in_interval.",
    values_to = "percent_in_interval"
  ) %>% 
  mutate(model_type = model.type3,
         purpose.lab = purpose3.lab)


#---------------------------Purpose 4 --------------------------------# 
#Read in previously saved file
HPD.4.summary_all <- read_csv(file = paste0(results_location, "HPD.summaries/HPD.summary_", date.of.simulation4, "_", purpose4, ".csv"))

HPD.4.summary.tidy <- HPD.4.summary_all %>%
  pivot_longer(
    cols = starts_with("percent"),
    names_to = "proportion_sampled",
    names_prefix = "percent_in_interval.",
    values_to = "percent_in_interval"
  ) %>%
  mutate(model_type = model.type4,
         purpose.lab = purpose4.lab)

#---------------Create dataframes to plot by sample size--------#
#Set eveyrthing to Null so the below scripts will run
HPD.samples1.1.4viz = HPD.samples2.1.4viz = HPD.samples3.1.4viz = HPD.samples4.1.4viz = HPD.samples1.2.4viz = HPD.samples2.2.4viz = HPD.samples3.2.4viz = HPD.samples4.2.4viz = HPD.samples1.3.4viz = HPD.samples2.3.4viz = HPD.samples3.3.4viz = HPD.samples4.3.4viz = HPD.samples1.4.4viz = HPD.samples2.4.4viz = HPD.samples3.4.4viz = HPD.samples4.4.4viz <- NULL

HPD.samples1.1.4viz <- HPD.1.summary.tidy %>% filter(proportion_sampled == "0.5_percent_sampled")
HPD.samples2.1.4viz <- HPD.1.summary.tidy %>% filter(proportion_sampled == "1_percent_sampled")
HPD.samples3.1.4viz <- HPD.1.summary.tidy %>% filter(proportion_sampled == "1.5_percent_sampled")
HPD.samples4.1.4viz <- HPD.1.summary.tidy %>% filter(proportion_sampled == "2_percent_sampled")

HPD.samples1.2.4viz <- HPD.2.summary.tidy %>% filter(proportion_sampled == "0.5_percent_sampled")
HPD.samples2.2.4viz <- HPD.2.summary.tidy %>% filter(proportion_sampled == "1_percent_sampled")
HPD.samples3.2.4viz <- HPD.2.summary.tidy %>% filter(proportion_sampled == "1.5_percent_sampled")
HPD.samples4.2.4viz <- HPD.2.summary.tidy %>% filter(proportion_sampled == "2_percent_sampled")

HPD.samples1.3.4viz <- HPD.3.summary.tidy %>% filter(proportion_sampled == "0.5_percent_sampled")
HPD.samples2.3.4viz <- HPD.3.summary.tidy %>% filter(proportion_sampled == "1_percent_sampled")
HPD.samples3.3.4viz <- HPD.3.summary.tidy %>% filter(proportion_sampled == "1.5_percent_sampled")
HPD.samples4.3.4viz <- HPD.3.summary.tidy %>% filter(proportion_sampled == "2_percent_sampled")

HPD.samples1.4.4viz <- HPD.4.summary.tidy %>% filter(proportion_sampled == "0.5_percent_sampled")
HPD.samples2.4.4viz <- HPD.4.summary.tidy %>% filter(proportion_sampled == "1_percent_sampled")
HPD.samples3.4.4viz <- HPD.4.summary.tidy %>% filter(proportion_sampled == "1.5_percent_sampled")
HPD.samples4.4.4viz <- HPD.4.summary.tidy %>% filter(proportion_sampled == "2_percent_sampled")


#Combine above dataframes, and re-order purpose as factors
all.samples1.4viz <- HPD.samples1.1.4viz %>% bind_rows(HPD.samples1.2.4viz, HPD.samples1.3.4viz, HPD.samples1.4.4viz) 
all.samples1.4viz$purpose.lab <- factor(all.samples1.4viz$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))

all.samples2.4viz <- HPD.samples2.1.4viz %>% bind_rows(HPD.samples2.2.4viz, HPD.samples2.3.4viz, HPD.samples2.4.4viz) 
all.samples2.4viz$purpose.lab <- factor(all.samples2.4viz$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))

all.samples3.4viz <- HPD.samples3.1.4viz %>% bind_rows(HPD.samples3.2.4viz, HPD.samples3.3.4viz, HPD.samples3.4.4viz) 
all.samples3.4viz$purpose.lab <- factor(all.samples3.4viz$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))

all.samples4.4viz <- HPD.samples4.1.4viz %>% bind_rows(HPD.samples4.2.4viz, HPD.samples4.3.4viz, HPD.samples4.4.4viz)
all.samples4.4viz$purpose.lab <- factor(all.samples4.4viz$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))

#For when we need everything together
all.4viz <- HPD.1.summary.tidy %>% bind_rows(HPD.2.summary.tidy, HPD.3.summary.tidy, HPD.4.summary.tidy)
all.4viz$purpose.lab <- factor(all.4viz$purpose.lab, levels = c(purpose1.lab, purpose2.lab, purpose3.lab, purpose4.lab))
```

```{r HPDI-and-Density-Plots, echo=FALSE}
p.Nfb <- all.4viz %>% dplyr::filter(parameter == "Nfb", proportion_sampled == "0.5_percent_sampled" | proportion_sampled == "2_percent_sampled") %>% 
   ggplot(aes(x = interval.scale)) +
   geom_point(aes(y = percent_in_interval, color = purpose.lab, fill = purpose.lab, shape = purpose.lab), size = 2.5, alpha = .7) + 
   geom_smooth(aes(y = percent_in_interval, color = purpose.lab, linetype = ), se = FALSE, size = 1.5, show.legend = FALSE) + 
   geom_line(aes(y = interval.scale), size = 1.5) + 
   ggtitle("A) Nf - breeders") + 
   labs(x = "HPDI",
        y = "Percent in HPDI") +
   theme_bw() + 
   theme(legend.title = element_blank()) + 
   scale_colour_brewer(palette = "Set1") +
   facet_wrap(~proportion_sampled) + 
  guides(color = guide_legend(nrow = 2))


p.Nm <- all.4viz %>% dplyr::filter(parameter == "Nm", proportion_sampled == "0.5_percent_sampled" | proportion_sampled == "2_percent_sampled") %>% 
  ggplot(aes(x = interval.scale)) +
  geom_point(aes(y = percent_in_interval, color = purpose.lab, fill = purpose.lab, shape = purpose.lab), size = 2.5, alpha = .7) + 
  geom_smooth(aes(y = percent_in_interval, color = purpose.lab, linetype = ), se = FALSE, size = 1.5, show.legend = FALSE) + 
  geom_line(aes(y = interval.scale), size = 1.5) + 
  ggtitle("C) Nm - total") + 
  labs(x = "HPDI",
       y = "Percent in HPDI") +
  theme_bw() + 
  theme(legend.title = element_blank()) + 
  scale_colour_brewer(palette = "Set1") +
  facet_wrap(~proportion_sampled)


p.surv <- all.4viz %>% dplyr::filter(parameter == "surv") %>% 
  ggplot(aes(x = interval.scale)) +
  geom_point(aes(y = percent_in_interval, color = purpose.lab, fill = purpose.lab, shape = purpose.lab), size = 2.5, alpha = .7) + 
  geom_smooth(aes(y = percent_in_interval, color = purpose.lab, linetype = ), se = FALSE, size = 1.5, show.legend = FALSE) + 
  geom_line(aes(y = interval.scale), size = 1.5) + 
  ggtitle("A) Survival") + 
  labs(x = "HPDI",
       y = "Percent in HPDI") +
  theme_bw() + 
  theme(legend.title = element_blank()) + 
  scale_colour_brewer(palette = "Set1") +
  facet_wrap(~proportion_sampled) +
  guides(color = guide_legend(nrow = 2))

#May want to add this: purpose.lab != purpose3.lab to the first line to filter out PO from lambda
p.lam <- all.4viz %>% dplyr::filter(parameter == "lam") %>% 
  ggplot(aes(x = interval.scale)) +
  geom_point(aes(y = percent_in_interval, color = purpose.lab, fill = purpose.lab, shape = purpose.lab), size = 2.5, alpha = .7) + 
  geom_smooth(aes(y = percent_in_interval, color = purpose.lab, linetype = ), se = FALSE, size = 1.5, show.legend = FALSE) + 
  geom_line(aes(y = interval.scale), size = 1.5) + 
  ggtitle("Lambda") + 
  labs(x = "HPDI",
       y = "Percent in HPDI") +
  theme_bw() + 
  theme(legend.title = element_blank()) + 
  scale_colour_brewer(palette = "Set1") +
  facet_wrap(~proportion_sampled)

p.psi <- all.4viz %>% dplyr::filter(parameter == "psi") %>% 
    ggplot(aes(x = interval.scale)) +
    geom_point(aes(y = percent_in_interval, color = purpose.lab, fill = purpose.lab, shape = purpose.lab), size = 2.5, alpha = .7) + 
    geom_smooth(aes(y = percent_in_interval, color = purpose.lab, linetype = ), se = FALSE, size = 1.5, show.legend = FALSE) + 
    geom_line(aes(y = interval.scale), size = 1.5) + 
    ggtitle("A) Percent biennial breeders (psi)") + 
    labs(x = "HPDI",
         y = "Percent in HPDI") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_colour_brewer(palette = "Set1") +
    facet_wrap(~proportion_sampled)

#-------------------Density plots-------------------------#
#Density plots
p2.Nfb <- results.all %>% dplyr::filter(parameter == "Nfb", samples.lab == samples1.lab | samples.lab == samples4.lab) %>% 
    ggplot(aes(x = relative_bias, color = purpose.lab, fill = purpose.lab)) +
    geom_density(alpha = 0.6) + 
    ggtitle("B) Nf - breeders") + 
    labs(x = "Relative bias of posterior median") +
    geom_vline(xintercept=c(0), linetype="dotted") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_fill_brewer(palette = "Set1") +
    xlim(-100, 100) + 
    facet_wrap(~samples.lab)

p2.Nm <- results.all %>% dplyr::filter(parameter == "Nm", samples.lab == samples1.lab | samples.lab == samples4.lab) %>% 
  ggplot(aes(x = relative_bias, color = purpose.lab, fill = purpose.lab)) +
  geom_density(alpha = 0.6) + 
  ggtitle("D) Nm - total") + 
  labs(x = "Relative bias of posterior median") +
  geom_vline(xintercept=c(0), linetype="dotted") +
  theme_bw() + 
  theme(legend.title = element_blank()) + 
  scale_fill_brewer(palette = "Set1") +
  xlim(-100, 100) + 
  facet_wrap(~samples.lab)

p2.surv <- results.all %>% dplyr::filter(parameter == "surv") %>% 
  ggplot(aes(x = relative_bias, color = purpose.lab, fill = purpose.lab)) +
  geom_density(alpha = 0.6) + 
  ggtitle("B)") + 
  labs(x = "Relative bias of posterior median") +
  geom_vline(xintercept=c(0), linetype="dotted") +
  theme_bw() + 
  theme(legend.title = element_blank()) + 
  scale_fill_brewer(palette = "Set1") +
  xlim(-25, 25) + 
  facet_wrap(~samples.lab)


p2.psi <- results.all %>% dplyr::filter(parameter == "psi") %>% 
    ggplot(aes(x = relative_bias, color = purpose.lab, fill = purpose.lab)) +
    geom_density(alpha = 0.6) + 
    ggtitle("B) Percent biennial breeders (psi)") + 
    labs(x = "Relative bias of posterior median") +
    geom_vline(xintercept=c(0), linetype="dotted") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_fill_brewer(palette = "Set1") +
    xlim(-100, 100) + 
    facet_wrap(~samples.lab)




p2.lam <- results.all %>% dplyr::filter(parameter == "lam") %>% 
    ggplot(aes(x = relative_bias, color = purpose.lab, fill = purpose.lab)) +
    geom_density(alpha = 0.6) + 
    ggtitle("Lambda") + 
    labs(x = "Relative bias of posterior median") +
    geom_vline(xintercept=c(0), linetype="dotted") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_fill_brewer(palette = "Set1") +
    xlim(-10, 10) + 
    facet_wrap(~samples.lab)


```

## Background info
One hundred different populations were simulated where 100% of females in the population bred biennially, with 5% of females also breeding in their off-year.

Each population was sampled at four different sampling intensities corresponding to 0.5, 1, 1.5, and 2 percent of the juvenile population each year over four consecutive years of sampling. Samples were either targeted to the young-of-year (YOY) portion of the population only, or included juveniles of all age classes. A pairwise comparisons matrix that included all possible positive and negative comparisons was used as input to a CKMR model that either a) assumed no prior information for breeding schedule (psi) *or* survival (phi), or b) assumed the breeding schedule was known without error (i.e. fixed to the truth) *and* included a tight prior on survival dnorm(mean = truth, sd = 0.02).  

## Figure 1: Accuracy of abundance estimates depends on sampling scheme and prior demographic information
**Sampling scheme:** Red and blue reflect sampling schemes that target YOY only; green and purple reflect sampling schemes where the entire juvenile population (ages 0-11) were available for sampling.  
**Prior information:** Red and green results come from a model that assumed no prior information for psi or survival; blue and purpose results come from a model that assumed psi was known without error and gave a tight prior to survival.  
**Main takeaways:** This figure shows results for the lowest and highest sample schemes employed only (i.e. 0.5% and 2% of the juvenile population). Here, we see a clear difference in model performance between males and females whereby female abundance is consistently biased upward. This is likely a consequence of changing the quantity we're estimating. For example, when all females breed biennially and no individuals breed in off-years, then the CKMR model is estimating the number of breeders. When females breed every year, then CKMR estimates the total number of females in the population. This is true even if only a subset of the population breeds in a given year, so long as the group of breeders each year is independent of the previous year. However, in this circumstance, breeding is intermediate between the two scenarios, so if I set the truth to the breeding population, as I did here, estimates are biased upwards. However, relative to the total population of adult females, estimates would be biased downwards. *Figuring out how to account for this in the model, and how to describe this, is a top priority.*

```{r print-N-plots, echo=FALSE, out.width = "120%", fig.height = 12}
#Male and female HPDI and relative bias for low and high sample sizes
ggarrange(p.Nfb, p2.Nfb, p.Nm, p2.Nm, common.legend = TRUE, nrow = 4, ncol = 1, legend = "bottom")
```

## Figure 2: Accuracy of survival estimates depends on sampling scheme and prior demographic information
**Sampling scheme:** Red and blue reflect sampling schemes that target YOY only; green and purple reflect sampling schemes where the entire juvenile population (ages 0-11) were available for sampling.  
**Prior information:** Red and green results come from a model that assumed no prior information for psi or survival (diffuse priors); blue and purpose results come from a model that assumed psi was known without error and gave a tight prior to survival.  
**Main takeaways:** When priors are diffuse (red and green), survival estimates have a tendency to get pulled upward. This tendency is amplified when sampling is targeted to YOY (red), likely because there are fewer age gaps represented in the data as well as fewer half-siblings available to inform survival estimates.

```{r print-surv-plots, echo=FALSE, out.width = "120%", fig.height = 12}
#Survival HPDI and relative bias for all four sample sizes
ggarrange(p.surv, p2.surv, common.legend = TRUE, nrow = 2, legend = "bottom")
```

## Figure 3: Accuracy and bias of psi depends on sampling scheme.
**Main takeaways:** When priors for psi and survival are diffuse, there appears to be a systemic bias in estimation of psi, which is amplified as sample size increases. The bias is minimal when juvenile sampling is targeted to the YOY portion of the population, but worsens when all age classes are sampled. I'm not sure why this is ...
```{r print-psi-plots, echo=FALSE, out.width = "120%", fig.height = 12}
ggarrange(p.psi, p2.psi, common.legend = TRUE, nrow = 2, legend = "bottom")
```

## Figure 4: Observed numbers of maternal - but not paternal - half-siblings depends on sampling scheme when females breed biennially.
**A and B:** Number of HSPs detected based on sampling scheme. **A)** For females that breed intermittently, more HSPs are found when sampling across juvenile age classes. When sampling is limited to YOY over four years of sampling, and females breed every other year, there are only two potential comparisons that would be expected to yield HSPs (cohorts 1 & 3; cohorts 2 & 4). When sampling across age classes, there are more cohorts available to yield HSPs. **B)** For males that breed annually, there is no difference in the number of HSPs detected based on sampling scheme. Note that for both males and females, the lowest sampling intensity results in fewer than 25 HSPs, which is half the recommended target of 50 for a reasonable CV. This is why results at this sampling intensity are so varied.  
**C and D:** Relative bias of abundance estimate by the percent difference between observed and expected HSPs.
Here, we see that as the observed number of HSPs deviates from expectations, results become more biased, as expected. Interestingly, we see an exponential rise in bias in the positive direction at the lowest sampling intensity, but this trend is not apparent in the negative direction. **C)** notice that when priors are diffuse, there remains a slight residual positive bias across sampling intensities when observed and expected HSPs match (i.e. x axis = 0) **D)** In contrast to scenario 1 where there were zero non-conformists, the bias remains for females when survival and psi are given informed priors. Because the expected number of HSPs for females depends on the true value of psi, I expect there is some issue with how I'm calculating the truth of psi.
**Main takeaways:** As more non-conformists are introduced into the female skipped-breeding population, the difference in observed HSPs between sampling schemes (all age classes vs YOY only) lessens compare to Scenario 1 where there were zero non-conformists. Also, it appears that there is a bias for females in all scenarios here when expected HSPs match observed HSPs, leading me to believe that I am doing something wrong in my calculation of the truth of psi (which is used in the calculation of expected HSPs)

```{r Kin pairs, echo=FALSE}
####---------------------Density plots of kin detected----------------------------------------------####

#Distribution of MHSPs
(Nfb_HSPs <- results.all %>% dplyr::filter(parameter == "Nfb",
                                           purpose.lab == purpose2.lab | purpose.lab == purpose4.lab) %>% 
  ggplot(aes(x = HSPs_detected, color = sampling.scheme, fill = sampling.scheme)) +
    geom_density(alpha = 0.6) + 
    ggtitle("A) Maternal HSPs detected") + 
    labs(x = "HSPs") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_fill_brewer(palette = "Set1") +
    facet_wrap(~samples.lab) + 
  scale_x_continuous(breaks = c(25, 50, 100, 150, 200, 250)))
                     

(Nm_HSPs <- results.all %>% dplyr::filter(parameter == "Nm",
                                          purpose.lab == purpose2.lab | purpose.lab == purpose4.lab) %>% 
  ggplot(aes(x = HSPs_detected, color = sampling.scheme, fill = sampling.scheme)) +
    geom_density(alpha = 0.6) + 
    ggtitle("B) Paternal HSPs detected") + 
    labs(x = "HSPs") +
    theme_bw() + 
    theme(legend.title = element_blank()) + 
    scale_fill_brewer(palette = "Set1") +
    facet_wrap(~samples.lab) + 
    scale_x_continuous(breaks = c(25, 50, 100, 150, 200, 250)))

#-----------------------Examine expected vs observed kin pairs--------------------
#Calculate % difference in expected vs observed kin
results.all2 <- results.all %>% mutate(HS_exp_obs_diff = (Exp_HSPs - HSPs_detected)/Exp_HSPs,
                                      PO_exp_obs_diff = (Exp_POPs - POPs_detected)/Exp_POPs) %>%
  mutate(PO_exp_obs_diff = replace_na(PO_exp_obs_diff, 0)) %>% 
  mutate(all_exp_obs_diff = HS_exp_obs_diff + PO_exp_obs_diff)



#----------------Make scatter plot of expected vs observed 
#Purpose 1
(EO1 <- results.all2 %>% dplyr::filter(parameter == "Nfb" | parameter == "Nm",
                                       purpose.lab == purpose1.lab | purpose.lab == purpose3.lab) %>% 
  ggplot(aes(x = HS_exp_obs_diff, y = relative_bias, fill = parameter, color = parameter)) +
  geom_point() +
  facet_wrap(~samples.lab) + 
  labs(title = "C) Expected vs Observed kin HSPs; diffuse priors", x = "Percent difference (Exp - Obs)/Exp", y = "Relative bias") + 
  theme(legend.title = element_blank()))

(EO2 <- results.all2 %>% dplyr::filter(parameter == "Nfb" | parameter == "Nm",
                                       purpose.lab == purpose2.lab | purpose.lab == purpose4.lab) %>% 
  ggplot(aes(x = HS_exp_obs_diff, y = relative_bias, fill = parameter, color = parameter)) +
  geom_point() +
  facet_wrap(~samples.lab) + 
  labs(title = "D) Expected vs Observed kin HSPs; informed priors", x = "Percent difference (Exp - Obs)/Exp", y = "Relative bias") + 
  theme(legend.title = element_blank()))
```