---
title: "Results for CKMR manuscript 07/01/2022"
output: 
  html_document:
    df_print: tibble
    toc: true
    toc_depth: 3
    fig_caption: yes
---

Get plots together
For Objective 2 (supplementary?): Multi-panel stacked (one column only) plot with 1.5% population sampled, 
top: estimating in present year; three separate density plots corresponding to sampling schemes; group by population growth?
middle: same as above, except estimating 5 yrs in the past
bottomr: same as above, except estimating 10 yrs in the past

Also, from objective 1, look at instances where the observed kin pairs matched the expected kin pairs, and compare year gaps (w/ histogram) between unbiased and biased estimates.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
#devtools::install_github("pconn/HierarchicalGOF/HierarchicalGOF")
#install.packages("ggmcmc")
library(tidyverse)
library(ggpubr)
library(RColorBrewer)
library(coda)
library(runjags)
library(ggmcmc)
library(viridis)
library(scales)
library(ggridges)

rm(list=ls())
today <- format(Sys.Date(), "%d%b%Y")

```



```{r set-file-locations and read in files, include = FALSE}
#------------- Simulation parameters and labels  ----------------#
#------------- Simulation parameters and labels  ----------------#
objective_1_MCMC_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.validation/Model.output/"
objective_1_results_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.validation/Model.results/"
objective_1_results_plots_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.1_model.validation/Model.results/figures/"

objective_2_MCMC_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.2_population.growth/Model.output/"
objective_2_results_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.2_population.growth/Model.results/"
objective_2_results_plots_location <- "G://My Drive/Personal_Drive/R/CKMR/Objective.2_population.growth/Model.results/figures/"

results_prefix <- "CKMR_results"
MCMC_prefix <- "CKMR_modelout"
parents_prefix <- "parents_breakdown/CKMR_parents.breakdown"
sample.prefix <- "sample_info/CKMR_sample.info"
pop.size.prefix <- "pop_size/CKMR_pop.size"
mom.comps.prefix <- "comparisons/mom.comps"
dad.comps.prefix <- "comparisons/dad.comps"


#-------------Objective 1.1 --------------------#
date.of.simulation.scenario_1.1Y <- "12Jul2022"
purpose.obj1.1Y <- "Obj1.1_model.validation_Target.YOY"
file.scenario_1.1Y <- "scenario_1.1_model.validation_Target.YOY"
purpose.obj1.1.labY <- "Target YOY"
model.type.obj1.1Y <- "HS.only"

date.of.simulation.scenario_1.1J <- "12Jul2022"
purpose.obj1.1J <- "Obj1.1_model.validation_sample.all.juvenile.ages"
file.scenario_1.1J <- "scenario_1.1_model.validation_sample.all.juvenile.ages"
purpose.obj1.1.labJ <- "Sample all juvenile ages"
model.type.obj1.1J <- "HS.only"

date.of.simulation.scenario_1.1A <- "13Jul2022"
purpose.obj1.1A <- "Obj1.1_model.validation_sample.ALL.ages"
file.scenario_1.1A <- "scenario_1.1_model.validation_sample.ALL.ages"
purpose.obj1.1.labA <- "Sample all age classes"
model.type.obj1.1A <- "HS + PO"


#-------------Objective 1.2 --------------------#
date.of.simulation.scenario_1.2Y <- "13Jul2022"
purpose.obj1.2Y <- "Obj1.2_model.validation_Target.YOY"
file.scenario_1.2Y <- "scenario_1.2_model.validation_Target.YOY"
purpose.obj1.2.labY <- "Target YOY"
model.type.obj1.2Y <- "HS.only"

date.of.simulation.scenario_1.2J <- "13Jul2022"
purpose.obj1.2J <- "Obj1.2_model.validation_sample.all.juvenile.ages"
file.scenario_1.2J <- "scenario_1.2_model.validation_sample.all.juvenile.ages"
purpose.obj1.2.labJ <- "Sample all juvenile ages"
model.type.obj1.2J <- "HS.only"

date.of.simulation.scenario_1.2A <- "13Jul2022"
purpose.obj1.2A <- "Obj1.2_model.validation_sample.ALL.ages"
file.scenario_1.2A <- "scenario_1.2_model.validation_sample.ALL.ages"
purpose.obj1.2.labA <- "Sample all age classes"
model.type.obj1.2A <- "HS + PO"


#-------------Objective 2.1 --------------------#
date.of.simulation.scenario_2.1Y <- "13Jul2022"
purpose.obj2.1Y <- "Obj2.1_lambda.trial_Target.YOY"
file.scenario_2.1Y <- "scenario_2.1_lambda.trial_Target.YOY"
purpose.obj2.1.labY <- "Target YOY"
model.type.obj2.1Y <- "HS.only"

date.of.simulation.scenario_2.1J <- "13Jul2022"
purpose.obj2.1J <- "Obj2.1_lambda.trial_sample.all.juvenile.ages"
file.scenario_2.1J <- "scenario_2.1_lambda.trial_sample.all.juvenile.ages"
purpose.obj2.1.labJ <- "Sample all juvenile ages"
model.type.obj2.1J <- "HS.only"

date.of.simulation.scenario_2.1A <- "13Jul2022"
purpose.obj2.1A <- "Obj2.1_lambda.trial_sample.ALL.ages"
file.scenario_2.1A <- "scenario_2.1_lambda.trial_sample.ALL.ages"
purpose.obj2.1.labA <- "Sample all age classes"
model.type.obj2.1A <- "HS + PO"


#-------------Objective 2.2.1 --------------------#
date.of.simulation.scenario_2.2.1Y <- "13Jul2022"
purpose.obj2.2.1Y <- c("Obj2.2.1_lambda.trial_Target.YOY_stablePopSimLambda","Obj2.2.1_lambda.trial_Target.YOY_variablePopSimLambda")
file.scenario_2.2.1Y <- c("scenario_2.2.1_lambda.trial_Target.YOY_stablePopSimLambda","scenario_2.2.1_lambda.trial_Target.YOY_variablePopSimLambda")
purpose.obj2.2.1.labY <- "Target YOY"
model.type.obj2.2.1Y <- "HS.only"

date.of.simulation.scenario_2.2.1J <- "13Jul2022"
purpose.obj2.2.1J <- c("Obj2.2.1_lambda.trial_sample.all.juvenile.ages_stablePopSimLambda", "Obj2.2.1_lambda.trial_sample.all.juvenile.ages_variablePopSimLambda")
file.scenario_2.2.1J <- c("scenario_2.2.1_lambda.trial_sample.all.juvenile.ages_stablePopSimLambda", "scenario_2.2.1_lambda.trial_sample.all.juvenile.ages_variablePopSimLambda")
purpose.obj2.2.1.labJ <- "Sample all juvenile ages"
model.type.obj2.2.1J <- "HS.only"

date.of.simulation.scenario_2.2.1A <- "13Jul2022"
purpose.obj2.2.1A <- c("Obj2.2.1_lambda.trial_sample.ALL.ages_stablePopSimLambda", "Obj2.2.1_lambda.trial_sample.ALL.ages_variablePopSimLambda")
file.scenario_2.2.1A <- c("scenario_2.2.1_lambda.trial_sample.ALL.ages_stablePopSimLambda", "scenario_2.2.1_lambda.trial_sample.ALL.ages_variablePopSimLambda")
purpose.obj2.2.1.labA <- "Sample all age classes"
model.type.obj2.2.1A <- "HS + PO"


#-------------Objective 2.2.2 --------------------#
#Named some of these with the wrong purpose. The popsim variable files did not include "variablePopSim" in the purpose, but the stable popsim simulations did include "stablePopSim". Also, the Target.YOY files were not capitalized.

date.of.simulation.scenario_2.2.2Y <- "14Jul2022"
purpose.obj2.2.2Y <- c("Obj2.2.2_lambda.trial_target.YOY_change.est.yr", "Obj2.2.2_lambda.trial_target.YOY_stablePopSimLambda_change.est.yr")
file.scenario_2.2.2Y <- c("scenario_2.2.2_lambda.trial_target.YOY_change.est.yr", "scenario_2.2.2_lambda.trial_target.YOY_stablePopSimLambda_change.est.yr")
purpose.obj2.2.2.labY <- "Target YOY"
model.type.obj2.2.2Y <- "HS.only"

date.of.simulation.scenario_2.2.2J <- "14Jul2022"
purpose.obj2.2.2J <- c("Obj2.2.2_lambda.trial_sample.all.juvenile.ages_change.est.yr", "Obj2.2.2_lambda.trial_sample.all.juvenile.ages_stablePopSimLambda_change.est.yr")
file.scenario_2.2.2J <- c("scenario_2.2.2_lambda.trial_sample.all.juvenile.ages_change.est.yr", "scenario_2.2.2_lambda.trial_sample.all.juvenile.ages_stablePopSimLambda_change.est.yr")
purpose.obj2.2.2.labJ <- "Sample all juvenile ages"
model.type.obj2.2.2J <- "HS.only"

date.of.simulation.scenario_2.2.2A <- "14Jul2022"
purpose.obj2.2.2A <- c("Obj2.2.2_lambda.trial_sample.ALL.ages_change.est.yr", "Obj2.2.2_lambda.trial_sample.ALL.ages_stablePopSimLambda_change.est.yr")
file.scenario_2.2.2A <- c("scenario_2.2.2_lambda.trial_sample.ALL.ages_change.est.yr", "scenario_2.2.2_lambda.trial_sample.ALL.ages_stablePopSimLambda_change.est.yr")
purpose.obj2.2.2.labA <- "Sample all age classes"
model.type.obj2.2.2A <- "HS + PO"


#----------------Set input file locations ------------------------------
#Population simulation files
PopSim.location <- "G://My Drive/Personal_Drive/R/CKMR/Population.simulations/"
PopSim.lambda.1 <- "lambda.1" # Can be lambda.1 or lambda.variable
PopSim.lambda.variable <- "lambda.variable"
PopSim.annual.breeding <- "annual.breeding" #Can be annual.breeding or biennial.breeding
PopSim.biennial.breeding <- "biennial.breeding"
Sampling.scheme.YOY <- "target.YOY" # Can be sample.all.juvenile.ages, target.YOY, or sample.ALL.ages
Sampling.scheme.juvs <- "sample.all.juvenile.ages" # Can be sample.all.juvenile.ages, target.YOY, or sample.ALL.ages
Sampling.scheme.all <- "sample.ALL.ages" # Can be sample.all.juvenile.ages, target.YOY, or sample.ALL.ages
date.of.PopSim <- "11Jul2022" # 11Jul2022
inSeeds <- "Seeds2022.04.15"

#---------------------------Objective 1 truth calculations----------------------#
#Confirmed that the population size is the same for all sampling schemes
obj1.popsize <- readRDS(file = paste0(PopSim.location, "pop.size_", date.of.PopSim, "_", inSeeds, "_", PopSim.lambda.1, "_", PopSim.annual.breeding, "_", Sampling.scheme.YOY))

#Confirmed that the comparisons are the same for scenarios 1.1 and 1.2
#Need to calculate mean truth over years that comparisons span
#YOY
scenario_1.1_mom.comps.YOY <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1Y, "_", inSeeds, "_", file.scenario_1.1Y)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.YOY <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1Y, "_", inSeeds, "_", file.scenario_1.1Y))

obj1_all.comps.YOY <- rbind(scenario_1.1_mom.comps.YOY, scenario_1.1_dad.comps.YOY)

#Juveniles
scenario_1.1_mom.comps.juvs <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1J, "_", inSeeds, "_", file.scenario_1.1J)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.juvs <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1J, "_", inSeeds, "_", file.scenario_1.1J))

obj1_all.comps.juvs <- rbind(scenario_1.1_mom.comps.juvs, scenario_1.1_dad.comps.juvs)

#All age classes
scenario_1.1_mom.comps.all <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1A, "_", inSeeds, "_", file.scenario_1.1A)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.all <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1A, "_", inSeeds, "_", file.scenario_1.1A))

obj1_all.comps.all <- rbind(scenario_1.1_mom.comps.all, scenario_1.1_dad.comps.all)


#----------------------Objective 2----------------------------#
#Confirmed that the comparisons are the same for scenarios 1.1 and 1.2
#Need to calculate mean truth over years that comparisons span
#YOY
scenario_1.1_mom.comps.YOY <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1Y, "_", inSeeds, "_", file.scenario_1.1Y)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.YOY <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1Y, "_", inSeeds, "_", file.scenario_1.1Y))

obj1_all.comps.YOY <- rbind(scenario_1.1_mom.comps.YOY, scenario_1.1_dad.comps.YOY)

#Juveniles
scenario_1.1_mom.comps.juvs <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1J, "_", inSeeds, "_", file.scenario_1.1J)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.juvs <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1J, "_", inSeeds, "_", file.scenario_1.1J))

obj1_all.comps.juvs <- rbind(scenario_1.1_mom.comps.juvs, scenario_1.1_dad.comps.juvs)

#All age classes
scenario_1.1_mom.comps.all <- readRDS(file = paste0(objective_1_results_location, mom.comps.prefix, "_", date.of.simulation.scenario_1.1A, "_", inSeeds, "_", file.scenario_1.1A)) %>% 
  dplyr::select(-BI)

scenario_1.1_dad.comps.all <- readRDS(file = paste0(objective_1_results_location, dad.comps.prefix, "_", date.of.simulation.scenario_1.1A, "_", inSeeds, "_", file.scenario_1.1A))

obj1_all.comps.all <- rbind(scenario_1.1_mom.comps.all, scenario_1.1_dad.comps.all)

```

```{r}
obj2_results


```